---
title: "Cymon information page"
output: pdf_document
fontsize: 5pt 
classoption: landscape
geometry: margin=0.5in

---

This pdf provides information about the following ip <http://tweakers.net> this website provides information about technology and is used by million of dutch people, we are going to use pythong and the CYNOM API to further examen this website.

First i will explain how I am using python to extract information about <http://tweakers.net> 

the first step to:

> Python:

>  * import json     #to import JSON library
>  + import cymon    #to impport CYMON API library

The next step is to add your api key:

> Python:

> * api = cymon.Cymon('a24ab574029d8a3a089f992b8a1c405dd68***')

the final step is to write the information into a file:

> Python:

> * with open('data.json', 'w') as outfile:
> *    json.dump(api.ip_events('213.239.154.20'), outfile)

As you notice there is an ip i am using the api.ip_events method in the CYMON API to get my dataset.

> R code:

> * The updated information on the site:

```{r}
library(jsonlite)
data <- fromJSON('/home/mchegzade/Documents/srt411/assignment1/data.json',  flatten=TRUE)

updated <- c(data$results$updated)
description <- c(data$results$description)
info.data <- data.frame(updated, description)

head(info.data)

```

> R code:

> * The type of danger information on the site:

```{r}
library(jsonlite)
data <- fromJSON('/home/mchegzade/Documents/srt411/assignment1/data.json',  flatten=TRUE)

created <- data$results$created

title <- data$results$title
tag <- data$results$tag
detail <- data$results$details_url

mal.data <- data.frame(created, tag, title)

head(mal.data)

```

This concludes the basic information what Cymon API provides
